RNA-seq from 4 cell populations

### 2021-08-04 deconvolution/fans4/molec_profiling.Rmd
bug fix

ggplot(tabList, aes(CT1, CT2, fill=corr)) + geom_tile() + theme_bw(15) + theme(aspect.ratio=1, plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + scale_fill_gradient(name = quote(pi[1]), low="white", high="red", limits=c(0, 1)) + geom_text(aes(label=format(corr, digits=3))) + xlab('') + ylab('') + ggtitle("Correlation between t-statistics")

C = matrix(1, 4,4)
rownames(C) = levels(info$CellType)
colnames(C) = levels(info$CellType)
tabList$CT1 = factor(tabList$CT1, levels(info$CellType))
tabList$CT2 = factor(tabList$CT2, levels(info$CellType))

for(i in 1:nrow(tabList)){
  C[tabList$CT1[i],tabList$CT2[i]] = tabList$corr[i]
  C[tabList$CT2[i],tabList$CT1[i]] = tabList$corr[i]
}

plot(hclust(as.dist(1-C)))
```

@@

>>>>

tabList$CT1 = factor(tabList$CT1, names(colorCodes)[1:4])
tabList$CT2 = factor(tabList$CT2, names(colorCodes)[1:4])

ggplot(tabList, aes(CT1, CT2, fill=corr)) + geom_tile() + theme_bw(15) + theme(aspect.ratio=1, plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + scale_fill_gradient(name = "Correlation", low="white", high="red", limits=c(0, 1)) + geom_text(aes(label=format(corr, digits=3))) + xlab('') + ylab('') + ggtitle("Correlation between t-statistics")

# C = matrix(1, 4,4)
# rownames(C) = levels(info$CellType)
# colnames(C) = levels(info$CellType)
# tabList$CT1 = factor(tabList$CT1, levels(info$CellType))
# tabList$CT2 = factor(tabList$CT2, levels(info$CellType))

# for(i in 1:nrow(tabList)){
#   C[tabList$CT1[i],tabList$CT2[i]] = tabList$corr[i]
#   C[tabList$CT2[i],tabList$CT1[i]] = tabList$corr[i]
# }

# plot(hclust(as.dist(1-C)))
```

```{r scatterPlots, dev="png"}
library(viridis)

# Compute two dimensional density
get_density <- function(x, y, n = 250) {
  dens <- MASS::kde2d(x = x, y = y, n = n)
  ix <- findInterval(x, dens$x)
  iy <- findInterval(y, dens$y)
  ii <- cbind(ix, iy)
  return(dens$z[ii])
}

# make scatter plot with 2D density using viridis colors
plotScatterDensity = function(value1, value2){

  # convert two vectors to a data frame
  df = data.frame(cbind(value1, value2))

  # determine limits of the plot
  lim = with(df, max(abs(c(value1, value2))))

  # Compute 2D density
  df$density <- get_density(df$value1, df$value2, n = 100)

  # Scatter plot colored by density
  ggplot(df, aes(value1, value2, color=density)) + geom_point(size=.4) + theme_bw(16) + theme(aspect.ratio=1, legend.position="bottom", plot.title = element_text(hjust = 0.5)) + geom_abline(color="red") + geom_vline(xintercept=0, col="grey40", linetype="dashed") + geom_hline(yintercept=0, col="grey40", linetype="dashed") + xlim(-lim, lim) + ylim(-lim, lim) + scale_color_viridis() + geom_smooth(method="lm", se=FALSE, color="darkorange")
}

# for all pairs of cell types
figList = lapply( 1:ncol(index), function(j){

  fig = with(df_tstat, plotScatterDensity(t.x, t.y))
  fig + theme(legend.position="none") + xlab(CT1) + ylab(CT2)
})

plot_grid(plotlist = figList, ncol=3, nrow=3)
```

```{r mashr}
library(mashr)

```{r zenith.disease}
plotZenith = function(df){

  df$Geneset = factor(df$Geneset, cls)
  df$label = ifelse(df$FDR < 0.05, '*', '')

  M = reshape2::dcast(df, coef ~ Geneset, value.var="delta")
  annot = M[,1:2]
  M = as.matrix(M[,-1])
  rownames(M) = annot$coef

  hcl2 <- hclust(dist(t(M)))
  df$Geneset = factor(df$Geneset, colnames(M)[hcl2$order])

  statMax = with(df, max(abs(delta/se)))

  ggplot(df, aes(coef, Geneset, fill=delta/se, label=label)) + geom_tile() + theme_classic() + scale_fill_gradient2(limits=c(-statMax, statMax), low="blue", mid="white", high="red", name="t-statistic") + theme(aspect.ratio = ncol/nrow, axis.text.x = element_text(angle = 90, vjust = 1, hjust=1), plot.title = element_text(hjust = 0.5)) + xlab('') + ylab('') + geom_text(vjust=1, hjust=0.5) + ggtitle("Compare cell types")
}

geneSets_GO = get_GeneOntology()

df_zenith = zenith_gsa(fitDisease[fitDisease$Amean > 0,], colnames(coef(fitDisease))[1:4], geneSets_GO, inter.gene.cor=0.01)

df = df_zenith[,.SD[order(PValue)[1:10],],by=c("coef")]
cls = unique(df$Geneset)
df = df_zenith[Geneset %in% df$Geneset,]

pdf("test.pdf")
plotZenith(df)
dev.off()

```{r zenith.disease.mSigDB}
geneSets_MSigDB = get_MSigDB(c('H', "C1", "C2", "C3", "C5", "C7"))

df_zenith = zenith_gsa(fitDisease[fitDisease$Amean > 0,], colnames(coef(fitDisease))[1:4], geneSets_MSigDB, inter.gene.cor=0.01)

df = df_zenith[,.SD[order(PValue)[1:10],],by=c("coef")]
cls = unique(df$Geneset)
df = df_zenith[Geneset %in% df$Geneset,]

plotZenith(df)
```

@@

# Integrate CommonMind Consortium
```{r load.cmc}

geneCounts_CMC = readRDS(synGet('syn22416410')$path)
info_CMC = readRDS(synGet('syn22416411')$path)
